\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-22 sections/results.tex
Add: Section for CC step in the supplementary

  % TODO: Supplementary work - Figure S4
  After the denoising, the sequences are subject to chimera checking.
  The \ac{micone} pipeline supports two different chimera checking methods, uchime and remove bimera.
  The uchime method is from \ac{qiime2}, whereas the remove bimera method is from the \ac{dada2} R package.
  We did not notice any significant difference between the two chimera checking methods, implying that they identify and remove mostly the same set of sequences as chimeras (Figure ???).

>>>>

  After the denoising, the sequences are subject to chimera checking.
  The \ac{micone} pipeline supports two different chimera checking methods, uchime and remove bimera.
  The uchime method is from \ac{qiime2}, whereas the remove bimera method is from the \ac{dada2} R package.
  We did not notice any significant difference between the two chimera checking methods (Figure~\ref{fig:figure_s4}), implying that they identify and remove mostly the same set of sequences as chimeras.

### 2022-04-22 sections/supplementary.tex
Add: Section for CC step in the supplementary

    % TODO: Figure S4 - Unifrac bar plot for CC methods
    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s4.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
        }
      \label{fig:figure_s4}
    \end{figure}
    \FloatBarrier
    \newpage

>>>>

    We find that the two chimera checking methods, uchime and remove bimera, produce similar outputs.
    This can be verified by comparing the output (representative sequence distributions) of the two chimera checking methods for each denoising method (Figure~\ref{fig:figure_s4}).
    We find that with the exception of de novo and open-reference under the unweighted UniFrac metric, all the other methods have low dissimilarity.
    This is especially true for the \ac{dada2} and Deblur methods which are the recommended denoising methods in the \ac{micone} pipeline.
    % TODO: Can we verify this?
    Therefore, we recommended remove bimera as the default chimera method if one is using \ac{dada2} and uchime when one is using Deblur, since these methods were developed for these respective algorithms.

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s4.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
        }
      \label{fig:figure_s4}
    \end{figure}
    \FloatBarrier
    \newpage
